---
title: "SemiconductorStatistics_Report 1"
author: "Caleb Leonard"
date: "September 14, 2025"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Statistics in Semiconductor Manufacturing: T-Tests

With the initial 10 presample data points taken, at 0.05 significance level, power of 0.85, and detecting a mean shift of 0.1 nm from the targeted 32 nm gate critical dimension in one direction, 47 total data points should be collected. This is shown in the R code below

```{r cars}
#alpha = 0.05
#beta = 0.15
#power = 0.85
#number of presamples = 10
#target gate dimension = 32 nm
#mean shift = 0.1 nm
#presamples = (31.6, 32.1, 31.9, 31.7, 32.2, 31.8, 32.0, 31.5, 31.9, 31.7)
#tool 1 data = (31.6, 32.1, 31.9, 31.7, 32.2, 31.8, 32.0, 31.5, 31.9, 31.7, 32.1, 32.0, 32.1, 32.3, 31.9, 31.9, 32.3, 32.2, 31.9, 32.1,31.9, 31.9, 32.1, 31.6, 31.6, 31.9, 31.8, 32.1, 31.8, 31.7, 32.3, 32.0, 32.0, 31.7, 31.9, 32.0, 31.7, 32.1, 31.9, 31.9, 31.9, 32.4, 32.0, 31.8, 32.2, 31.7, 31.9)

presamples<-c(31.6, 32.1, 31.9, 31.7, 32.2, 31.8, 32.0, 31.5, 31.9, 31.7)
sd(presamples) #determine standard deviation of presample data
power.t.test(n=NULL,delta=0.1,sd=0.2221111,sig.level=0.05,
             power=.85,type="one.sample",alternative="two.sided")
```
After taking 37 more measurements of wafers produced with Tool 1, it was determined the mean of gate critical dimension is 31.936 nm

```{r}
tool1data<-c(31.6, 32.1, 31.9, 31.7, 32.2, 31.8, 32.0, 31.5, 31.9, 31.7, 32.1, 32.0, 32.1, 32.3, 31.9, 31.9, 32.3, 32.2, 31.9, 32.1,31.9, 31.9, 32.1, 31.6, 31.6, 31.9, 31.8, 32.1, 31.8, 31.7, 32.3, 32.0, 32.0, 31.7, 31.9, 32.0, 31.7, 32.1, 31.9, 31.9, 31.9, 32.4, 32.0, 31.8, 32.2, 31.7, 31.9)
t.test(tool1data, alternative="two.sided", mu=32)
hist(tool1data, main="presamples", xlab="observations", ylab = "frequency", col="red")
boxplot(tool1data, main="presamples",col="yellow")
```

To determine if Tool 1 and Tool 2 produce wafers with the same mean gate critical dimension, the following R code was used to determine a sample size of 14 measurements need to be taken from Tool 2.

```{r}
power.t.test(n=NULL,delta=0.2,sd=0.2079146,sig.level=0.05,
             power=.90,type="one.sample",alternative="two.sided")

```

